---
title: "DV_FinalProject"
author: "ENK"
date: "April 29, 2015"
output: html_document
---
Created by: Natasha Halfin, Evan Johnston, and Kaylyn Zvonek 

```{r, echo=TRUE}
library("ggplot2")
library("gplots")
library("bitops")
library("knitr")
library("jsonlite")
library("ggthemes")
library("RCurl")
library("reshape2")
library("tidyr")
library("dplyr")
library("grid")

source("../01 Data/Data.R")
source("../02 Data Wrangling/DataWrangling.R")
#source("../03 Visualizations/Visualizations.R")
```


For our project, we chose to work with three datasets. One contains data on the top 5000 companies in the U.S., the second contains state employment data, and the third data set describes housing data by state. Our goal was to cover as much material as possible that reflected the material covered in class, including data blending, data joins, beautiful plotting, data wrangling, SQL crosstabs, and advanced table calculations.

Below is a snapshot of the dataframes for each dataset prior to any data manipulation.

Top Companies Data

```{r, eval = TRUE, echo=TRUE}
data.frame(head(dfTOPCOMPANIES))
```

State Employment Data
```{r, eval = TRUE, echo=TRUE}
data.frame(head(dfSTATETOTALS))
```

State Housing Data
```{r, eval = TRUE, echo=TRUE}
data.frame(head(dfSTATEHOUSING))
```


DATA WRANGLINGS

```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfSTATEHOUSINGTOTALS))
```

DATA WRANGLING 3 
```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfTopCompanies2))
```



```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfTopCompanies3))
```


R DATASET AND TABLEAU WORKBOOK2
```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfNormalized))

```

R DATASET AND TABLEAU WORKBOOK3
```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfSTATEHOUSINGTOTALS3))
```

```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfRANKREVENUE))
```

```{r, eval=TRUE, echo=TRUE}
data.frame(head(dfRANKPOPDENSITY))
```